Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-04-04 ProbabilisticCoherence.tex
Correction made to earlier changes about R as restriction matrix, further cleaning up of definition of probabilisitic forecast reconciliation

Definition~\ref{def:reconpoint}, actually defines an entire family of forecast reconciliation methods including many methods currently extant in the literature. To provide a geometric interpretation, we introduce an $n \times (n-m)$ matrix $\bm{R}$ whose columns span the null space $\mathfrak{s}_{\perp}$.  The matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$. However, since $\bm{R}$ is not unique, the columns of any given $\bm{R}$ matrix can also be thought of as `directions' along which incoherent point forecasts are projected onto the coherent space. For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$ is the vector $(1,-1,-1)$, which is orthogonal to the columns of $\bm{S}$ in the usual sense of Euclidean geometry.
%$$ 
%\bm{S} = 
%\begin{pmatrix} 
%1& 1 \\ 1 & 0 \\ 0&1 
%\end{pmatrix} 
%\quad \text{and} \quad 
%\bm{R} = 
%\begin{pmatrix}  
%1 \\ -1 \\ -1 
%\end{pmatrix}.
%$$ 
%
%Further let $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively. Then $\bm{B}=\{\bm{s}_1,\dots,\bm{s}_m, \bm{r}_1,\dots,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$. Now, using the insights of Definition~\ref{def:reconpoint}, we can use the following steps to reconcile the point forecasts.

@@

  Let $(\mathbb{R}^n, \mathscr{F}^{\mathbb{R}^n}, \hat{\nu})$ be an incoherent probability triple that characterises forecast uncertainty in for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$.  Let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m $ be a linear mapping.  Let $(\mathbb{R}^m, \mathscr{F}^{\mathbb{R}^m}, \nu)$ be a probability triple defined on $\mathbb{R}^m$ where $\nu$ has the following property:
  \begin{equation}
  \nu(A) = \hat{\nu}(g^{-1}(A)), \quad \forall \quad A \in \mathscr{F}^{\mathbb{R}^m}\,.
  \end{equation}
  Here $g^{-1}(A)$ denotes the pre-image of the measurable set $A$, that is $g^{-1}(A):=\left\{\bm{y}\in \mathbb{R}^n:\bm{Gy}\in A \right\}$. In words, the preimage $g^{-1}(A)$ is the set of all points in $\mathbb{R}^n$ that $g(.)$ maps to a point in $A$.
  \begin{definition} \label{def:reconprob}
  We define $\tilde{\nu}$ as the reconciled probability measure of $\hat{\nu}$ with respect to the mapping $g(.)$ if the following holds
  \begin{equation}
  \tilde{\nu}(s(A)) = \nu(A)= \hat{\nu}(g^{-1}(A)) \qquad \forall A \in \mathscr{F}^{\mathbb{R}^m},
  \end{equation}
  where $\tilde{\nu}(\cdot)$ is a probability measure on the $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_\mathfrak{s}$.
\end{definition}

We now discuss how this definition can be used in practice to obtain reconciled probabilistic forecasts for hierarchical time series.

>>>>

Definition~\ref{def:reconpoint}, actually defines an entire family of forecast reconciliation methods including many methods currently extant in the literature. To provide a geometric interpretation, we introduce an $n \times (n-m)$ matrix $\bm{R}$ whose columns span the null space $\mathfrak{s}_{\perp}$.  For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$ is the vector $(1,-1,-1)$, which is orthogonal to the columns of $\bm{S}$ in the usual sense of Euclidean geometry.  In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$. In general, the columns of any given $\bm{R}$ matrix can also be thought of as `directions' along which incoherent point forecasts are projected onto the coherent space, and these directions need not be orthogonal to $\mathfrak{s}$. 
%$$ 
%\bm{S} = 
%\begin{pmatrix} 
%1& 1 \\ 1 & 0 \\ 0&1 
%\end{pmatrix} 
%\quad \text{and} \quad 
%\bm{R} = 
%\begin{pmatrix}  
%1 \\ -1 \\ -1 
%\end{pmatrix}.
%$$ 
%
%Further let $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively. Then $\bm{B}=\{\bm{s}_1,\dots,\bm{s}_m, \bm{r}_1,\dots,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$. Now, using the insights of Definition~\ref{def:reconpoint}, we can use the following steps to reconcile the point forecasts.

@@

  Let $(\mathbb{R}^n, \mathscr{F}^{\mathbb{R}^n}, \hat{\nu})$ be an probability triple, that is not necessarily coherent and that characterises forecast uncertainty for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$.  Let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m $ be a linear mapping.  Let $(\mathbb{R}^m, \mathscr{F}^{\mathbb{R}^m}, \nu)$ be a probability triple defined on $\mathbb{R}^m$ where $\nu$ has the following property:
  \begin{equation}
  \nu(A) = \hat{\nu}(g^{-1}(A)), \quad \forall \quad A \in \mathscr{F}^{\mathbb{R}^m}\,.
  \end{equation}
  Here $g^{-1}(A):=\left\{\bm{y}\in \mathbb{R}^n:g(\bm{y})\in A \right\}$ is the pre-image of $A$, that is the set of all points in $\mathbb{R}^n$ that $g(.)$ maps to a point in $A$.
  \begin{definition} \label{def:reconprob}
  We define the reconciled probability measure of $\hat{\nu}$ with respect to the mapping $g(.)$ as a probability measure $\tilde{\nu}$ on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_\mathfrak{s}$ where the following holds
  \begin{equation}
  \tilde{\nu}(s(A)) = \nu(A)= \hat{\nu}(g^{-1}(A)) \qquad \forall A \in \mathscr{F}^{\mathbb{R}^m}\,.
  \end{equation}
\end{definition}

We now discuss how this definition can be used in practice to obtain reconciled probabilistic forecasts for hierarchical time series.   Recall that the case of forecast reconciliation could be broken down into three steps.  In the first via a change of basis $\hat{\bm{y}_{t+h|t}}$ is transformed into coordinates $\tilde{\bm{b}_{t+h|t}}$ and $\tilde{\bm{a}_{t+h|t}}$.  In the second, $\tilde{\bm{a}_{t+h|t}}$ is discarded and $\tilde{\bm{b}_{t+h|t}}$ are kept as the bottom level reconciled forecasts.  In the third reconciled forecasts for the entire hierarchy are recovered via $\tilde{\bm{y}_{t+h|t}}=\bm{S}\tilde{\bm{b}_{t+h|t}}$.  We now outline these three steps for probabilistic forecasts and demonstrate how they correspond to Definition~\ref{def:reconprob}.
